\TheTitle

### 2019-08-15 Paper1/results.tex
minor fix formula
smaller changes intro and results continued

\subsection{2D Euler equations with a one dimensional uncertainty}
We start by quantifying the effects of an uncertain angle of attack $\phi\sim U(0.75,1.75)$ for a NACA0012 profile computed with different methods. The stochastic Euler equations in two dimensions are given by
\begin{align*}
\partial_t
\begin{pmatrix}
\rho \\ \rho v_1 \\ \rho v_2 \\ \rho e
\end{pmatrix}
+\partial_{x_1}
\begin{pmatrix}
\rho v_1 \\ \rho v_1^2 +p \\ \rho v_1 v_2 \\  v_1 (\rho e+p)
\end{pmatrix}
+\partial_{x_2}
\begin{pmatrix}
\rho v_2 \\ \rho v_1 v_2 \\ \rho v_2^2+p \\ v_2 (\rho e+p)
\end{pmatrix}
=\bm{0}.
\end{align*}
These equations determine the time evolution of the conserved variables $(\rho,rho \bm v, rho e)$, i.e. density, momentum and energy. A closure for the pressure $p$ is given by
\begin{align*}
p = (\gamma-1)\rho\left(e-\frac12(v_1^2+v_2^2)\right).
\end{align*}
Since the the fluid of the following test cases is air, we choose the heat capacity ratio $\gamma$ to be $1.4$. The spatial mesh discretizes the flow domain around the airfoil. At the airfoil boundary $\Gamma_{0}$, we use the Euler slip condition $\bm v^T\bm n = 0$, where $\bm n$ denotes the surface normal. At a sufficiently large distance away from the airfoil, we assume a far field flow with a given Mach number $Ma = 0.8$, pressure $p = 101\;325$ Pa and a temperature of $273.15$ K. Now the angle of attack $\phi$ is uniformly distributed in the interval of $[0.75,1.75]$ degrees. I.e. we choose $\phi(\xi) = 1.25 + 0.5\xi$ where $\xi\sim U(-1,1)$. As commonly done, the initial condition is equal to the far field boundary values. Consequently, the wall condition at the airfoil is violated and will correct the flow solution. The computational domain is a circle with a diameter of $40$ meters. In the center, the NACA0012 airfoil with a length of one meter is located. The discretization is composed of a coarsely refined far field and a finely resolved region around the airfoil, since we are interested in the flow solution at the airfoil. Altogether, the mesh consists of 22361 triangular elements.

@@

Note that in the case of SC, the error cannot be recorded without destroying the non-intrusive framework and adding extra costs, which is why we only plot the final error and the corresponding run time. To account for the fact that sparse grids need to be used in higher dimensions, we use Clenshaw-Curtis quadrature rules to compute the different solutions. Stochastic-Collocation uses quadrature levels $2,3$ and $4$, which corresponds to $5,9$ and $17$ quadrature points. All adaptive methods use gPC polynomials of order 2 to 9 (i.e. 3 to 10 moments). Order 2 uses a level 2, orders 3 to 6 use a level 3 and orders 8 and 9 use a level 4 quadrature rule. The remaining methods have been computed with a level 4 quadrature rule.

@@

@@

\newgeometry{top=1.5cm, left=1.0cm}
\begin{figure}[h!]
\centering
	\begin{subfigure}{0.33\linewidth}
		\centering
				\includegraphics[scale=0.25]{figs/Euler1DPlots10/{EulerSC4-17Res1e-6_errors_ERho}.png}
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{0.33\linewidth}
		\centering
				\includegraphics[scale=0.25]{figs/Euler1DPlots10/{euler2D_nacaCoarse_sg_n9_sg4_s05_aoa_errors_ERho}.png}
		\label{fig:sub2}
	\end{subfigure}
		\begin{subfigure}{0.33\linewidth}
		\centering
				\includegraphics[scale=0.25]{figs/Euler1DPlots10/{euler2D_nacaCoarse_ipm_n9_sg4_s05_aoa_errors_ERho}.png}
		\label{fig:sub2}
	\end{subfigure}
	\caption{Errors E$[\rho]$ for SC$^{17}$, SG$_{10}$, IPM$_{10}$ (from left to right).}
	\label{fig:ErrorsERho}
\end{figure}

\begin{figure}[h!]
\centering
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/varRho/{euler2D_nacaCoarse_sc_n5_s05_aoa_var}.png}
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/varRho/{euler2D_nacaCoarse_sg_n5_nq10_s05_aoa_var}.png}
		\label{fig:sub2}
	\end{subfigure}%
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/varRho/{euler2D_nacaCoarse_ipm_n5_nq10_s05_aoa_var}.png}
		\label{fig:sub1}
	\end{subfigure}

	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/varRho/{euler2D_nacaCoarse_caipm_n10_nq15_s05_aoa_var}.png}
		\label{fig:sub2}
	\end{subfigure}%
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/varRho/{euler2D_nacaCoarse_caosipm_n10_nq15_s05_aoa_var}.png}
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/varRho/{euler2D_nacaCoarse_sc_n50_s05_aoa_var_legend}.png}
		\label{fig:sub2}
	\end{subfigure}%
	\caption{Var$[\rho]$ (from top left to bottom right) SC, SG, IPM, caIPM, caosIPM, reference solution.}
	\label{fig:Obstacles2D}
\end{figure}

%%% error plots %%%
\begin{figure}[h!]
\centering
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/expectedRho/errors/{euler2D_nacaCoarse_sc_n5_s05_aoa_error_legend}.png}
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/expectedRho/errors/{euler2D_nacaCoarse_sg_n5_nq10_s05_aoa_error_legend}.png}
		\label{fig:sub2}
	\end{subfigure}%
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/expectedRho/errors/{euler2D_nacaCoarse_ipm_n5_nq10_s05_aoa_error_legend}.png}
		\label{fig:sub1}
	\end{subfigure}

	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/expectedRho/errors/{euler2D_nacaCoarse_caipm_n10_nq15_s05_aoa_error_legend}.png}
		\label{fig:sub2}
	\end{subfigure}%
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/expectedRho/errors/{euler2D_nacaCoarse_caosipm_n10_nq15_s05_aoa_error_legend}.png}
		\label{fig:sub1}
	\end{subfigure}
	\caption{E$[\rho]$ distance to reference solution (from top left to bottom right) SC, SG, IPM, caIPM, caosIPM.}
	\label{fig:Obstacles2D}
\end{figure}

\begin{figure}[h!]
\centering
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/varRho/errors/{euler2D_nacaCoarse_sc_n5_s05_aoa_var_error_legend}.png}
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/varRho/errors/{euler2D_nacaCoarse_sg_n5_nq10_s05_aoa_var_error_legend}.png}
		\label{fig:sub2}
	\end{subfigure}%
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/varRho/errors/{euler2D_nacaCoarse_ipm_n5_nq10_s05_aoa_var_error_legend}.png}
		\label{fig:sub1}
	\end{subfigure}

	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/varRho/errors/{euler2D_nacaCoarse_caipm_n10_nq15_s05_aoa_var_error_legend}.png}
		\label{fig:sub2}
	\end{subfigure}%
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/varRho/errors/{euler2D_nacaCoarse_caosipm_n10_nq15_s05_aoa_var_error_legend}.png}
		\label{fig:sub1}
	\end{subfigure}
	\caption{Var$[\rho]$ distance to reference solution (from top left to bottom right) SC, SG, IPM, caIPM, caosIPM.}
	\label{fig:Obstacles2D}
\end{figure}
\newgeometry{top=2.5cm, bottom=2.5cm}

>>>>

\subsection{2D Euler equations with a one dimensional uncertainty}
We start by quantifying the effects of an uncertain angle of attack $\phi\sim U(0.75,1.75)$ for a NACA0012 profile computed with different methods. The stochastic Euler equations in two dimensions are given by
\begin{align*}
\partial_t
\begin{pmatrix}
\rho \\ \rho v_1 \\ \rho v_2 \\ \rho e
\end{pmatrix}
+\partial_{x_1}
\begin{pmatrix}
\rho v_1 \\ \rho v_1^2 +p \\ \rho v_1 v_2 \\  v_1 (\rho e+p)
\end{pmatrix}
+\partial_{x_2}
\begin{pmatrix}
\rho v_2 \\ \rho v_1 v_2 \\ \rho v_2^2+p \\ v_2 (\rho e+p)
\end{pmatrix}
=\bm{0}.
\end{align*}
These equations determine the time evolution of the conserved variables $(\rho,\rho \bm v, \rho e)$, i.e. density, momentum and energy. A closure for the pressure $p$ is given by
\begin{align*}
p = (\gamma-1)\rho\left(e-\frac12(v_1^2+v_2^2)\right).
\end{align*}
Since the the fluid of the following test cases is air, we choose the heat capacity ratio $\gamma$ to be $1.4$. The spatial mesh discretizes the flow domain around the airfoil. At the airfoil boundary $\Gamma_{0}$, we use the Euler slip condition $\bm v^T\bm n = 0$, where $\bm n$ denotes the surface normal. At a sufficiently large distance away from the airfoil, we assume a far field flow with a given Mach number $Ma = 0.8$, pressure $p = 101\;325$ Pa and a temperature of $273.15$ K. Now the angle of attack $\phi$ is uniformly distributed in the interval of $[0.75,1.75]$ degrees. I.e. we choose $\phi(\xi) = 1.25 + 0.5\xi$ where $\xi\sim U(-1,1)$. As commonly done, the initial condition is equal to the far field boundary values. Consequently, the wall condition at the airfoil is violated and will correct the flow solution. The computational domain is a circle with a diameter of $40$ meters. In the center, the NACA0012 airfoil with a length of one meter is located. The discretization is composed of a coarsely refined far field and a finely resolved region around the airfoil, since we are interested in the flow solution at the airfoil. Altogether, the mesh consists of 22361 triangular elements.

@@

Note that in the case of SC, the error cannot be recorded without violating the non-intrusive framework and adding extra costs, which is why we only plot the final error and the corresponding run time. To account for the fact that sparse grids need to be used in high dimensional problems, we use Clenshaw-Curtis quadrature rules to compute the different solutions. Stochastic-Collocation uses quadrature levels $2,3$ and $4$, which corresponds to $5,9$ and $17$ quadrature points. All adaptive methods use gPC polynomials of order 2 to 9 (i.e. 3 to 10 moments). Order 2 uses a level 2, orders 3 to 6 use a level 3 and orders 8 and 9 use a level 4 quadrature rule. The remaining methods have been computed with a level 4 quadrature rule.

@@

\begin{center}
\begin{tabular}{ | m{3cm} || m{0.9cm} | m{0.9cm} | m{0.9cm} | m{0.9cm} | m{0.9cm} | m{0.9cm} | m{0.9cm} | m{0.9cm} | m{0.9cm} | m{0.9cm} | } 
\hline
residual \eqref{eq:residualSteady} & 5e-06 & 4e-06 & 3e-06 & 2e-06 & 1e-06 & 9e-07 & 8e-07 & 7e-07 & 6e-07 & 5e-07  \\ 
\hline
error E[$\rho$] in e-03 & 1.506 & 1.464 & 1.438 & 1.401 & 1.368 & 1.360 & 1.359 & 1.358 & 1.358 & 1.357  \\ 
\hline
error Var[$\rho$] in e-03 & 1.339 & 1.332 & 1.292 & 1.248 & 1.217 & 1.215 & 1.214 & 1.213 & 1.213 & 1.213  \\ 
\hline
\end{tabular}
\end{center}

@@

\begin{figure}[h!]
\centering
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/Euler1DPlots10/{euler2D_nacaCoarse_refadosipm_n2-9_sg2-4_s05_aoa_oneRet_ERho}.png}
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/Euler1DPlots10/{euler2D_nacaCoarse_refadosipm_n2-9_sg2-4_s05_aoa_oneRet_VarRho}.png}
		\label{fig:sub2}
	\end{subfigure}%
	\begin{subfigure}{0.33\linewidth}
		\centering
		\includegraphics[scale=0.2]{figs/Euler1DPlots10/{euler2D_nacaCoarse_refadosipm_n2-9_sg2-4_s05_aoa_oneRet_refinementLevel}.png}
		\label{fig:sub1}
	\end{subfigure}
	\caption{E$[\rho]$, Var$[\rho]$ and refinement level for readosIPM$_{2-9}$}
	\label{fig:ERhoVarRho5}
\end{figure}

\begin{figure}[h!]
\centering
	\begin{subfigure}{0.33\linewidth}
		\centering
				\includegraphics[scale=0.2]{figs/Euler1DPlots10/{EulerSC4-17Res1e-6_errors_ERho}.png}
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{0.33\linewidth}
		\centering
				\includegraphics[scale=0.2]{figs/Euler1DPlots10/{euler2D_nacaCoarse_sg_n9_sg4_s05_aoa_errors_ERho}.png}
		\label{fig:sub2}
	\end{subfigure}
		\begin{subfigure}{0.33\linewidth}
		\centering
				\includegraphics[scale=0.2]{figs/Euler1DPlots10/{euler2D_nacaCoarse_ipm_n9_sg4_s05_aoa_errors_ERho}.png}
		\label{fig:sub2}
	\end{subfigure}
	\caption{Errors E$[\rho]$ for SC$^{17}$, SG$_{10}$, IPM$_{10}$ (from left to right).}
	\label{fig:ErrorsERho}
\end{figure}
\newgeometry{top=2.5cm, left=2.5cm}
